Type-Safe Modular Parsing

### 2017-01-03 paper/sections/ObjectAlgebras.tex
Revised S5. Related work to be revised.

On the other hand, the data variants can be extended by inheriting \lstinline{ExprAlg} and adding new cases only. Now we extend the language
with variables. A new Object Algebra interface \lstinline{VarAlg} is defined as follows:

@@

\lstinputlisting[linerange=100-128]{../Scala/Parser/src/PaperCode/Overview/OA.scala}% APPLY:linerange=OVERVIEW_OA_MULTI_SYNTAX
Besides lexing, the trait \lstinline{TypedLamOAParser} also introduces parsers for types, and the new case for expressions. For the same reason,
we use \lstinline{pTypedLamT} and \lstinline{pTypedLamE} as copies of current \lstinline{pT} and \lstinline{pE}, recursively. \lstinline{pT} and \lstinline{pE} are actually the parsers for recursion.

@@

\lstinputlisting[linerange=132-134]{../Scala/Parser/src/PaperCode/Overview/OA.scala}% APPLY:linerange=OVERVIEW_OA_MULTI_SYNTAX_CLIENT
Pretty-printing the parsed results just works as expected.

>>>>

On the other hand, the data variants can be extended by inheriting \lstinline{ExprAlg} and adding new cases only. Now we extend the language
with variables. A new Object Algebra interface \lstinline{VarAlg} is defined as follows:\haoyuan{Can we use var instead of varE?}

@@

\lstinputlisting[linerange=100-129]{../Scala/Parser/src/PaperCode/Overview/OA.scala}% APPLY:linerange=OVERVIEW_OA_MULTI_SYNTAX
Besides lexing, the trait \lstinline{TypedLamOAParser} also introduces parsers for types, and the new case for expressions. For the same reason,
we use \lstinline{pTypedLamT} and \lstinline{pTypedLamE} as copies of current \lstinline{pT} and \lstinline{pE}, recursively. \lstinline{pT} and \lstinline{pE} are actually the parsers for recursion.

@@

\lstinputlisting[linerange=133-135]{../Scala/Parser/src/PaperCode/Overview/OA.scala}% APPLY:linerange=OVERVIEW_OA_MULTI_SYNTAX_CLIENT
Pretty-printing the parsed results just works as expected.

### 2017-01-03 paper/sections/OpenRecursion.tex
Revised S5. Related work to be revised.

\lstinputlisting[linerange=24-30]{../Scala/Parser/src/PaperCode/SampleParser.scala}% APPLY:linerange=OPENRECURSION_FIB

@@

\lstinputlisting[linerange=34-40]{../Scala/Parser/src/PaperCode/SampleParser.scala}% APPLY:linerange=OPENRECURSION_FIB2
\bruno{Fix should be replaces by Open. Please coordinate with Huang to
ensure that your code and his code are coherent (i.e you use same
names and same conventions),}
\noindent This alternative implementation has an extra argument
\lstinline{self}, which serves as an explicit self-reference. In the
definition of the function, direct recursive calls are replaced by
calls to the self reference.

@@

\lstinputlisting[linerange=44-44]{../Scala/Parser/src/PaperCode/SampleParser.scala}% APPLY:linerange=OPENRECURSION_FIB_FIX

@@

\lstinputlisting[linerange=20-20]{../Scala/Parser/src/PaperCode/SampleParser.scala}% APPLY:linerange=OPENRECURSION_FIX
\bruno{can be defined in a single line.}
\noindent Note that the function \lstinline{f} has a by-name parameter
of type \lstinline{"=>} \lstinline{T"}. This is necessary to ensure
termination of well-founded recursive calls. In such cases,
there are some base cases (like the first two in
\lstinline{fib2}) which stop the recursion in their branches, and the
evaluation is finally reduced to those cases.

@@

\bruno{We may want to use a better example than what is next.}
Suppose now we want to make use of open recursion for additional operations. We first define a combinator which combines the results of two generators in a pair:
\lstinputlisting[linerange=48-51]{../Scala/Parser/src/PaperCode/SampleParser.scala}% APPLY:linerange=OPENRECURSION_COMPOSE

Using Scala implicit class, \lstinline{*} can be used as an infix operator for composition in convenience.
Then we define a generator which prints out a number as a string:
\lstinputlisting[linerange=55-55]{../Scala/Parser/src/PaperCode/SampleParser.scala}% APPLY:linerange=OPENRECURSION_SHOW

@@

Next we define a more general combinator \lstinline{merge} for open recursion. It is similar to the \lstinline{*} above, but instead of putting two values in a pair by default, \lstinline{merge} takes a parameter called \lstinline{op}, which tells the associative operation of two results. The definition is straightforward:
\lstinputlisting[linerange=59-60]{../Scala/Parser/src/PaperCode/SampleParser.scala}% APPLY:linerange=OPENRECURSION_MERGE

>>>>

\lstinputlisting[linerange=-]{}% APPLY:linerange=OPENRECURSION_FIB

@@

\lstinputlisting[linerange=-]{}% APPLY:linerange=OPENRECURSION_FIB2
\bruno{Fix should be replaces by Open. Please coordinate with Huang to
ensure that your code and his code are coherent (i.e you use same
names and same conventions),}
\noindent This alternative implementation has an extra argument
\lstinline{self}, which serves as an explicit self-reference. In the
definition of the function, direct recursive calls are replaced by
calls to the self reference.

@@

\lstinputlisting[linerange=-]{}% APPLY:linerange=OPENRECURSION_FIB_FIX

@@

\lstinputlisting[linerange=-]{}% APPLY:linerange=OPENRECURSION_FIX
\bruno{can be defined in a single line.}
\noindent Note that the function \lstinline{f} has a by-name parameter
of type \lstinline{"=>} \lstinline{T"}. This is necessary to ensure
termination of well-founded recursive calls. In such cases,
there are some base cases (like the first two in
\lstinline{fib2}) which stop the recursion in their branches, and the
evaluation is finally reduced to those cases.

@@

\bruno{We may want to use a better example than what is next.}
Suppose now we want to make use of open recursion for additional operations. We first define a combinator which combines the results of two generators in a pair:
\lstinputlisting[linerange=-]{}% APPLY:linerange=OPENRECURSION_COMPOSE

Using Scala implicit class, \lstinline{*} can be used as an infix operator for composition in convenience.
Then we define a generator which prints out a number as a string:
\lstinputlisting[linerange=-]{}% APPLY:linerange=OPENRECURSION_SHOW

@@

Next we define a more general combinator \lstinline{merge} for open recursion. It is similar to the \lstinline{*} above, but instead of putting two values in a pair by default, \lstinline{merge} takes a parameter called \lstinline{op}, which tells the associative operation of two results. The definition is straightforward:
\lstinputlisting[linerange=-]{}% APPLY:linerange=OPENRECURSION_MERGE
